analysis

### 2020-05-29 analysis.Rmd
added GAM surface analysis

### Per-capita floral resource abundance ~ elevation
ggplot(abund_div, aes(elev.mean, log(fl.per.bb))) +
  geom_point(alpha = 0.5) +
  geom_smooth() +
  facet_grid(year~phase, scales = "free") +
  ylab("log(fl-per-bb)") +
  xlab("Elevation") +
  theme_light()

@@

>>>>

### Per-capita floral resource abundance ~ elevation
ggplot(abund_div, aes(elev.mean, log(fl.per.bb))) +
  geom_point(alpha = 0.5) +
  #stat_summary(aes(y = log(fl.per.bb), group=1), fun.y=mean, colour="black", geom="point",group=1) +
  geom_smooth() +
  facet_grid(year~phase, scales = "free") +
  ylab("log(fl-per-bb)") +
  xlab("Elevation") +
  theme_light()

@@

### GAM surface plots of abundance and diversity metrics (just for fun)
```{r}
library(mgcv)
library(mgcViz)

percap_surf <- bam(fl.per.bb ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div, year == 2012),
                   #family = "poisson", # I think Poisson is the right call since richness data = count data
                   method = "REML")

webass_surf <- bam(web.asymmetry ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div, year == 2012),
                   #family = "poisson", # I think Poisson is the right call since richness data = count data
                   method = "REML")

bb.rich_surf <- bam(bb.rich ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div, year == 2012),
                   #family = "poisson", # I think Poisson is the right call since richness data = count data
                   method = "REML")

bb.abund_surf <- bam(bb.abund ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div, year == 2012),
                   #family = "poisson", # I think Poisson is the right call since richness data = count data
                   method = "REML")

fl.rich_surf <- bam(fl.rich ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div, year == 2012),
                   #family = "poisson", # I think Poisson is the right call since richness data = count data
                   method = "REML")

fl.abund_surf <- bam(fl.abund ~ te(gdd.cum, elev.mean, bs = "tp", m = 2, k = 10),
                   data = filter(abund_div, year == 2012),
                   #family = "poisson", # I think Poisson is the right call since richness data = count data
                   method = "REML")

s1 <- getViz(percap_surf)
plot(s1)

s2 <- getViz(webass_surf)
plot(s2)

s3 <- getViz(bb.rich_surf)
plot(s3)

s4 <- getViz(bb.abund_surf)
plot(s4)

s5 <- getViz(fl.rich_surf)
plot(s5)

s6 <- getViz(fl.abund_surf)
plot(s6)
```
